### 2021-03-01 paper.Rmd
-

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)
- Physics (Ursula)
- Bioinformatics (Stuart)

- High-d shapes/distributions: normal, skewed, outliers, (Di from tutorial notes)

>>>>

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)
- Physics (Ursula)
- Bioinformatics (Stuart)
- High-d shapes/distributions: normal, skewed, outliers, (Di from tutorial notes)
